%description: Math 290 HW Template
\documentclass[10pt]{article}  %What kind of document (article) and what size

%Packages to load which give you useful commands
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{titlesec}
\usepackage{titling}
%Sets the margins

\textwidth = 7 in
\textheight = 9.5 in
\oddsidemargin = -0.3 in
\evensidemargin = -0.3 in
\topmargin = -0.4 in
\headheight = 0.0 in
\headsep = 0.0 in

\setlength{\droptitle}{-1cm}  % Adjust this value to move the title up/down


\renewcommand{\abstractname}{Overview}
\titlespacing{\section}{0pt}{0.1cm}{0.1cm}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\small\bfseries}{\thesubsubsection}{1em}{}

\title{What is a Website and How is it Deployed?}
\author{Test Your Learning}
\date{Fall 2024}
\renewcommand{\maketitle}{
    \begin{center}
        {\LARGE \textbf{\thetitle}}\\[12pt] % Title with no space below
        {\large \theauthor}\\[12pt] % Author with no space below
    \end{center}
}

\newcommand{\question}[1]{
\section{#1}
\fbox{\makebox[0.95\linewidth]{\rule{0pt}{0.5in}}}

}
\begin{document}

\maketitle
\begin{abstract}
    In this workshop we will learn everything about websites from some basic HTML to running a massively scalable website on a Linux cluster. Take this exam before the workshop and at the end to see how much you've learned.
\end{abstract}

\question{What language is used for the content of a webpage?}
\question{What language is used for the style of a webpage?}
\question{What language is used for adding things like button clicks to a webpage?}
\question{What is a browser?}
\question{Name 5 popular browsers}
\question{What is a static website?}
\question{Name 2 popular tools for making static websites}
\question{What is a dynamic website?}
\question{What is an SQL database?}
\question{What is SQL?}
\question{Name 3 SQL databases}
\question{Is sqlite3 a popular database? Why?}
\question{What is a NoSQL database?}
\question{Name 2 NoSQL databases}
\question{What is an IP address?}
\question{What is a LAN?}
\question{What is the internet?}
\question{What is a webserver(hardware)?}
\question{What is a webserver(software)?}
\question{Name the two most popular webserver softwares}
\question{What is a backend web framework?}
\question{Name 4 languages you could use to make a backend?}
\question{Name 2 popular Python backend frameworks}
\question{Name a popular C\# backend framework}
\question{Name a popular Kotlin backend framework}
\question{Name a popular Java backend framework}
\question{What is a single page application?}
\question{What is a frontend framework?}
\question{What language is used to make frontend frameworks?}
\question{Name 3 popular front end frameworks}
\question{What is a REST API?}
\question{What does REST stand for?}
\question{What does API stand for?}
\question{What is JSON?}
\question{What is containerization?}
\question{What is a virtual machine?}
\question{What is Docker?}
\question{What are some reason(s) Docker is better than a VM?}
\question{What are some reason(s) Docker is worse than a VM?}
\question{Is Linux a great operating system for running websites?}
\question{What is a reverse proxy?}
\question{What is Kubernetes?}


 \end{document}
